The Weakly Nonlinear Magnetorotational Instability

### 2016-09-02 paper/widegap_mri_paper.tex
updated future work bullet points.

There are several avenues for future work, including
\begin{itemize}
\item detailed comparison to specific experimental apparatus. will gle dynamics be visible? 
\item the vertical dimension is incompletely modeled - stratification, etc
\item explore saturation property dependence of system on rotation profile 
\item different field geometries (e.g. radially varying)
\item other radial boundary conditions
\item drop axisymmetry
\item comparison to simulation in both weakly and strongly nonlinear regimes
\end{itemize}

>>>>

There are several avenues for future work, including
\begin{itemize}
\item detailed comparison to a specific experimental apparatus. Will gle dynamics be visible? 
\item inclusion of vertical stratification to the base state
\item different field geometries (e.g. radially varying)
\item comparing the saturation properties of different rotation profiles
\item expanding radial boundary conditions to mimimic astrophysical disks rather than TC devices
\item comparison to simulation in both weakly and strongly nonlinear regimes
\end{itemize}
